\documentclass[a4paper,10pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

% Custom command for project entries
\newcommand{\projectentry}[5]{
  \noindent
  \textbf{#1} \hfill
  \href{#4}{Link} $|$ \href{#5}{GitHub} \\
  #2 \\
  \textit{Tools used:} #3
  \vspace{6pt} % Adjust the spacing between projects as needed
}

\begin{document}

\pagestyle{empty}

\begin{center}
  \textbf{\LARGE Suraj Kareppagol} \\
  \vspace{6pt}
  \href{surajkareppagol.social@gmail.com}{Email} $|$ \href{https://github.com/surajkareppagol}{Github} $|$ \href{https://suraj-kareppagol.web.app/}{Portfolio} $|$ +91 8088346618
\end{center}

\section*{Skills}
\begin{itemize}[label=--,left=0pt, align=left]
  \item \textbf{Programming languages:} C, C++, Python, Javascript, TypeScript, Rust
  \item \textbf{Libraries/Frameworks:} React, ExpressJS, VueJS, NodeJS
  \item \textbf{Tools/Platforms:} Linux, VS Code, Git
  \item \textbf{Databases:} PostgreSQL, MongoDB
\end{itemize}

\section*{Projects}
\projectentry{HGR}{
  Designed and implemented cross-platform API for hand gesture recognition using MediaPipe.
}{
  Python, MediaPipe, OpenCV, Git
}{https://github.com/surajkareppagol/HGR}{https://github.com/surajkareppagol/HGR}

\projectentry{CREPL}{
  Developed CREPL, a Python-based REPL program for C language execution.
}{
  C, Python, Rich, Git
}{https://github.com/surajkareppagol/CREPL}{https://github.com/surajkareppagol/CREPL}

\projectentry{Libefile}{
  Developed a C Library for file manipulation, providing abstract functions to simplify working with files.
}{
  C, Make, Git
}{https://github.com/surajkareppagol/Lib-efile}{https://github.com/surajkareppagol/Lib-efile}

\projectentry{AURPy}{
  Created an Arch AUR Helper with Python, integrating Aurweb RPC interface. Enables package installation from AUR and facilitates package searches.
}{
  Python, Rich, Git
}{https://github.com/surajkareppagol/AURPy}{https://github.com/surajkareppagol/AURPy}

\projectentry{AniASCII}{
  Implemented a C Program for animating ASCII arts, offering a variety of animations.
}{
  C, Make, Git
}{https://github.com/surajkareppagol/ANIASCII}{https://github.com/surajkareppagol/ANIASCII}

\projectentry{CreateTT}{
  Developed a Python TUI time table builder using the rich module for enhanced visuals and a modular design.
}{
  Python, Rich, Git
}{https://github.com/surajkareppagol/CreateTT}{https://github.com/surajkareppagol/CreateTT}

\projectentry{Beginning End Sort}{
  Developed a sorting algorithm with $O(n^2)$ time complexity, inspired by Quick Sort and Selection Sort.
}{
  C, Git
}{https://github.com/surajkareppagol/BESort}{https://github.com/surajkareppagol/BESort}

\projectentry{XML To JSON Parser}{
  Created a Python script to convert XML to JSON, forming a collection of parsers.
}{
  Python, XML, JSON, Git
}{https://github.com/surajkareppagol/Parser}{https://github.com/surajkareppagol/Parser}

\projectentry{File Sharer}{
  Engineered a simple CRUD based File and Message sharing web application.
}{
  HTML, CSS, SCSS, JavaScript, NodeJS, ExpressJS, Pug, MongoDB, Git
}{https://github.com/surajkareppagol/FileSharer}{https://github.com/surajkareppagol/FileSharer}

\projectentry{Numerical Methods}{
  Implemented mathematical numerical methods in C Language.
}{
  C, Git
}{https://github.com/surajkareppagol/Numerical-Methods}{https://github.com/surajkareppagol/Numerical-Methods}

\projectentry{Tic Tac Toe}{
  Developed a classic Tic Tac Toe game with a minimal and beautiful UI, offering both Light and Dark themes.
}{
  HTML, CSS, SCSS, JavaScript, Git
}{https://surajkareppagol.github.io/Tic-Tac-Toe/}{https://github.com/surajkareppagol/Tic-Tac-Toe}

\section*{Academics}
Computer Organization, Data structures, Algorithms, Operating Systems, Database System, Computer Graphics, Computer Networks, Cryptography, Artificial Intelligence and Machine Learning, Automata Theory, Compiler Design

\section*{Experience}
\noindent
\textbf{4G5G Consultants | Software Engineering Intern} \hfill Karnataka | June 2023 - November 2023
\begin{itemize}[left=0pt]
  \item Internship at 4G5G Consultants, a Wireless Technology company.
  \item Tested and optimized RAN configurations, contributing to enhanced network performance.
  \item Gained proficiency in Linux, CLI tools, Version Control Systems, and cloud technologies.
\end{itemize}

\section*{Education}
\noindent
\textbf{Jain College Of Engineering, Belagavi, Karnataka} \hfill July 2020 - July 2024 \\
Computer Science And Engineering (B.E) \hfill CGPA: 9.28

\section*{Certificates}
\begin{itemize}[label=--,left=0pt]
  \item \href{https://www.hackerrank.com/certificates/4549bfcbe000}{Python - Hackerrank}
  \item \href{https://www.hackerrank.com/certificates/c045fb9d30e6}{CSS - Hackerrank}
\end{itemize}

\end{document}
